Figures

### 2020-04-14 manuscript/appendix.Rmd
stash text

<!-- How do reported values of lake depth compare to depth calculated from detailed bathymetry? -->
<!-- Given the importance of depth-dependent processes in determining lake function, it is encouraging that reported maximum depth values are closely aligned with “true” depth values calculated from bathymetry. This suggests that uncertainty or bias in reported lake depths is not likely responsible for the poor performance of prior depth prediction studies. -->

>>>>

<!-- Reported maximum depth values were very similar to calculated maximum depth values as evidenced by their alignment along a 1:1 line (Figure 3). Conversely, the alignment between reported and calculated mean depth values was more messy. In particular, the calculated mean depth of Maine lakes appeared to be consistently underestimated compared to reported values.  -->

<!-- Given the importance of depth-dependent processes in determining lake function, it is encouraging that reported maximum depth values are closely aligned with “true” depth values calculated from bathymetry. This suggests that uncertainty or bias in reported lake depths is not likely responsible for the poor performance of prior depth prediction studies. -->
